Relocating a Cluster of Earthquakes Using a Single Seismic Station

### 2012-12-14 paper2/paper2.tex
from SAGM day at GA

\begin{figure}
%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\noindent\includegraphics[width =
20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\caption{Example 3 - Statistical measures of error in the
optimization solutions for the 2D synthetic cases when all (gray)
and best (black) results are considered. The statistics
$\Delta_{max}$ and $\Delta_\mu$  are the maximum and mean coordinate
error, respectively. The bottom subplot shows the average minimum
number of branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

@@

% This is the version using hypoDD with SVD
\begin{figure}
\noindent\includegraphics[width =
20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
Number of constrainable events,$nE$ in
the CWI and hypoDD inversions as a function of the stations
considered (top). Mean (middle) and maximum (bottom) of the difference
computed between the reduced station inversion results (CWI and
hypoDD) and the complete hypoDD locations for all 308 events. } \label{fig-statremoval_summarystats}
\end{figure}
%%=========================================================================

>>>>

\begin{figure}
%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\noindent\includegraphics[width =
20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\caption{Example 3 - Statistical measures of error in the
 solutions for the 2D synthetic cases when all and best
optimization results are considered. The statistics $\Delta_{max}$
and $\Delta_\mu$  are the maximum and mean coordinate error,
respectively. The bottom subplot shows the average minimum number of
branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

@@

% This is the version using hypoDD with SVD
\begin{figure}
\noindent\includegraphics[width =
20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
Number of constrainable events $nE$ in the CWI and hypoDD inversions
as a function of the stations considered (top). Mean (middle) and
maximum (bottom) of the difference computed between the reduced
station inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. } \label{fig-statremoval_summarystats}
\end{figure}
%%=========================================================================
